Arrows for Parallel Computation

### 2018-01-07 paper/content/main.tex
added short intro to section 3
typo

	\end{flushright}\section{Background}
	\label{sec:background}
	As a introduction, we here give a short overview over Arrows and GpH, the |Par| Monad, and Eden, the three parallel Haskells which we base our DSL on.
	\input{arrows}
	\input{parallelHaskells}
	%\pagebreak
	%\pagebreak
	%\pagebreak
	\input{parrows}
	%\pagebreak
	\input{basicSkeletons}
	%\pagebreak
	\input{syntacticSugar}
	%\pagebreak
	\input{futures}
	%\pagebreak
	\input{mapSkeletons}
	%\pagebreak
	\input{topologySkeletons}
	%\pagebreak
	\input{benchmarks}
	%%\pagebreak
	\input{conclusion}
	%\pagebreak
        \bibliographystyle{jfp}
	\bibliography{references,main}
        \appendix
	\input{utilityFunctions}
\end{document}

>>>>

	\end{flushright}\section{Background}
	\label{sec:background}
	As an introduction, we here give a short overview over Arrows and GpH, the |Par| Monad, and Eden, the three parallel Haskells which we base our DSL on.
	\input{arrows}
	\input{parallelHaskells}
	%\pagebreak
	%\pagebreak
	%\pagebreak
	\input{parrows}
	%\pagebreak
	\input{basicSkeletons}
	%\pagebreak
	\input{syntacticSugar}
	%\pagebreak
	\input{futures}
	%\pagebreak
	\input{mapSkeletons}
	%\pagebreak
	\input{topologySkeletons}
	%\pagebreak
	\input{benchmarks}
	%%\pagebreak
	\input{conclusion}
	%\pagebreak
        \bibliographystyle{jfp}
	\bibliography{references,main}
        \appendix
	\input{utilityFunctions}
\end{document}
